Twists of supersymmetric gauge theories

### 2020-01-15 paper.tex
Editing through S1

\begin{table}[!h]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_16}
\end{table}

@@

\subsection{Conventions}
Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.  For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.

@@

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data of:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{\mr{BV}} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

@@

\begin{remark}
We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
\end{remark}

@@

\begin{definition}
A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
\end{itemize}
Together, these data must satisfy the equation
\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
\end{definition}

@@

In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories. All theories we consider in this section are $\ZZ$-graded, i.e. the space $E$ of fields will be completely even with respect to the $\ZZ/2$-grading.

@@

\begin{remark}
We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
\end{remark}

@@

Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.

@@

\begin{rmk}
This is a special case of generalized BF theory: the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure. 
\end{rmk}

We may also couple a $\beta\gamma$ system to a generalized $BF$ theory as follows.

\begin{example}
Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ a dg representation of $\fg$. Consider the dg Lie algebra
\[\cL = \fg\oplus V[-1]\]
with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$. The space of fields in the corresponding generalized BF theory will be denoted by
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
\end{example}

@@

\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}

The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.

@@

We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.

\begin{example}
For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
\end{example}

\begin{example}
For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
\end{example}

@@

We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$. Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$. The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$. Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
\end{proof}

@@

So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.

@@

The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component. Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.

@@

\begin{remark}
Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
where the $\ZZ/2$-grading on $E$ is the total grading.
\end{remark}

@@

We begin with a description of certain pure supersymmetric Yang--Mills theories. Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification. Fix a $\ZZ/2$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.

@@

The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$. So, it gives rise to a $\ZZ/2$-graded holomorphic theory. A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$. Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
\end{itemize}

@@

The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$. So, it gives rise to a $\ZZ/2$-graded holomorphic theory. A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$. Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
\end{itemize}

@@

% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading). 

@@

\begin{thm}
The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.  That is, the theory with the space of fields $\mr{Map}(\CC^3, U/\!/\gg)$, where $U/\!/\gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$. 
\label{thm:6dholomorphictwist}
\end{thm}

@@

\begin{proof}
We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.  That is, by applying Proposition \ref{CS__diml_red_prop} to the family of twists in 7-dimensions.
\end{proof}

@@

\begin{theorem} \label{5d_holo_twist_theorem}
The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U/\!/G)$.
\end{theorem}

@@

\begin{theorem} \label{4d_2_holo_twist_thm}
The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U/\!/\gg))$.
\end{theorem}

@@

\begin{theorem} \label{4d_Donaldson_twist_thm}
The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U/\!/\gg)_{\mr{Hod}})$.  
\end{theorem}

@@

\begin{theorem} \label{4d_11_twist_thm}
The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U/\!/\gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

@@

\begin{theorem} \label{3d_4_holo_A_twist_thm}
The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U/\!/\gg))$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U/\!/\gg)_{\mr{Hod}})$.
\end{theorem}

@@

\begin{theorem} \label{3d_2_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U/\!/\gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

@@

In this paper we will extensively use the theory of spinors. Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing. Recall that the Clifford algebra $\Cl(V)$ is defined to be the quotient of the tensor algebra on $V$ by the relation
\[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
Consider a $\ZZ/2$-graded Clifford module $M=M^+\oplus M^-$. Denote the Clifford action by $\rho(v)\in\eend(M)$. We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
\[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
for any $Q_1, Q_2\in M$ and $v\in V$. From now on we denote $M^+=\Sigma$ and $M^-=\Sigma^*$. We define the $\Gamma$-pairings
\[\Gamma\colon\Sym^2(\Sigma)\longrightarrow V,\qquad \Gamma\colon\Sym^2(\Sigma^*)\longrightarrow V\]
by
\begin{equation}
(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
\label{eq:Gammaspinorpairing}
\end{equation}

>>>>

\begin{table}[!h]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_16}
\end{table}

@@

\subsection{Conventions}
Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.  For an element $x$ we denote by $|x|\in\ZZ/2\ZZ$ the total degree.

@@

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data of:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{\mr{BV}} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

@@

\begin{remark}
We will also consider \defterm{$\ZZ/2\ZZ$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2\ZZ$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
\end{remark}

@@

\begin{definition}
A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
\end{itemize}
Together, these data must satisfy the equation
\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
\end{definition}

@@

In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories. All theories we consider in this section are $\ZZ$-graded, i.e. the space $E$ of fields will be completely even with respect to the $\ZZ/2\ZZ$-grading.

@@

\begin{remark} \label{mapping_stack_remark}
The mapping stack above has a precise meaning in the language of derived algebraic geometry \chris{Let's say a few words about where the terminology comes from at least, even if for us it's just shorthand.  I can add this later.  I should also remark on the fact that we can pull the $T^*[d]$ out to a $T^*[k]$, with $k=-1$ if $X,Y,M$ are vector spaces.}  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.  The language of the mapping stack will simply be used as a compact way of referring to the theory above. 
\end{remark}

@@

We will see many $BF$ theories as the output when we twists a supersymmetric gauge theories.
In fact, a special case of the definition above also arises when twisting theories of matter.  We will refer to as a generalized $\beta\gamma$ system, extending the usual 2d $\beta \gamma$ system.

@@

\begin{rmk}
This is indeed a special case of generalized BF theory: the generalized $\beta\gamma$ system appears as generalized $BF$ theory with the $L_\infty$ algebra given by $\fg = V[-1]$, with trivial $L_\infty$ structure. 
\end{rmk}

We may also couple a $\beta\gamma$ system to a more general generalized $BF$ theory as follows.

\begin{example}
Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ is a dg representation of $\fg$. Consider the dg Lie algebra
\[\cL = \fg\oplus V[-1]\]
with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$. The space of fields in the corresponding generalized BF theory will be denoted using the mapping stack notation (as in Remark \ref{mapping_stack_remark}) as
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
\end{example}

@@

\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.

@@

We may also consider a $\ZZ/2\ZZ$-graded version of the above theory where $\fg$ is merely $\ZZ/2\ZZ$-graded.

\begin{example}
For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern-Simons theory with the BV action
\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern-Simons theory.  This has the same BV action, where now $A$ is a (not necessarily homogeneous) differential form on $M$.  If $d$ is not 3 this theory is only $\ZZ/2\ZZ$-graded.
\end{example}

\begin{example}
For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
As in the previous example, this still makes sense if $X$ is a Calabi-Yau $d$-fold with $d$ odd, as a $\ZZ/2\ZZ$-graded theory.
\end{example}

@@

We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$. Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$. The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q_{\mr{BV}}$. Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
\end{proof}

@@

So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2\ZZ$-graded Clifford module.

@@

The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component. Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2\ZZ$-graded Clifford module.

@@

\begin{remark}
Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2\ZZ$-graded classical field theory
\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
where the $\ZZ/2\ZZ$-grading on $E$ is the total grading.
\end{remark}

@@

We begin with a description of certain pure supersymmetric Yang--Mills theories. Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification. Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.

@@

The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$. So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory. A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$. Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
\end{itemize}

@@

The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$. So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory. A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$. Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
\end{itemize}

@@

% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2\ZZ$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading). 

@@

\begin{thm}
The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.  That is, the theory with the space of fields $\mr{Map}(\CC^3, U\ham \gg)$, where $U\ham \gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$. 
\label{thm:6dholomorphictwist}
\end{thm}

@@

\begin{proof}
We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.  That is, by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 7-dimensions.
\end{proof}

@@

\begin{theorem} \label{5d_holo_twist_theorem}
The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
\end{theorem}

@@

\begin{theorem} \label{4d_2_holo_twist_thm}
The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U\ham \gg))$.
\end{theorem}

@@

\begin{theorem} \label{4d_Donaldson_twist_thm}
The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U\ham \gg)_{\mr{Hod}})$.  
\end{theorem}

@@

\begin{theorem} \label{4d_11_twist_thm}
The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U\ham \gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

@@

\begin{theorem} \label{3d_4_holo_A_twist_thm}
The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
\end{theorem}

@@

\begin{theorem} \label{3d_2_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

@@

In this paper we will extensively use the theory of spinors. Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing. Recall that the Clifford algebra $\Cl(V)$ is defined to be the quotient of the tensor algebra on $V$ by the relation
\[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
Consider a $\ZZ/2\ZZ$-graded Clifford module $M=M^+\oplus M^-$. Denote the Clifford action by $\rho(v)\in\eend(M)$. We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
\[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
for any $Q_1, Q_2\in M$ and $v\in V$. From now on we denote $M^+=\Sigma$ and $M^-=\Sigma^*$. We define the $\Gamma$-pairings
\[\Gamma\colon\Sym^2(\Sigma)\longrightarrow V,\qquad \Gamma\colon\Sym^2(\Sigma^*)\longrightarrow V\]
by
\begin{equation}
(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
\label{eq:Gammaspinorpairing}
\end{equation}
